Computing astrophysical inferences with diffusive nested sampling

### 2014-02-03 ms.tex
The problem with copying

The second common strategy is to use MCMC. Since the remaining live points are
known to exceed the likelihood threshold, they can be used to initialise an
MCMC run. This strategy is very simple but has known issues.

>>>>

The second common strategy is to use MCMC. Since the remaining live points are
known to exceed the likelihood threshold, they can be used to initialise an
MCMC run. This strategy is very simple but has known problems. For example,
suppose the likelihood function has two separate modes, and it impossible for
MCMC to mix between the two modes. Suppose also that NS is being run with two
points, and there is one point in each mode. The worst point will be discarded
(and its information saved elsewhere), and the new point will be generated by
copying the other point and running MCMC. However, even though the two modes
are completely equivalent, the copying operation will remove one of the modes,
and it will never return.
